Fivebranes

### 2022-02-22 fivebranes/index.tex
fixed typos

\[
\begin{tikzcd}
  &  \ul{\rm even} & \ul{\rm odd} \\
 \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
 \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}& \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[l, "\del"]
\end{tikzcd}
.\]

@@

          where $a, b, c, k, l \geq 0$.
    \item $V_{\mu}$ is spanned by
          \begin{align}
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{1}},\
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l-1}\del_{z_{1}}\text{ where }a > 0, b,c,k,l \geq 0 \\
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,b-1,c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{2}}, \ \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(0,b-1,c)}w_{1}^{k}w_{2}^{l-1}\del_{z_{2}}\text{ where }b > 0,c,k,l \geq 0 \\
            & \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,0,c-1)}w_{1}^{k-1}w_{2}^{l}\del_{z_{3}}, \ \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-l\delta^{(0,0,c-1)}w_{1}^{k}w_{2}^{l-1}\del_{z_{3}}\text{ where } c > 0,k,l \geq 0 \\
            & \delta^{(0,0,0)}w_{2}^{l}\del_{w_1}, \ \delta^{(0,0,0)}w_{1}^{k}\del_{w_2}\text{ where }k,l \geq 0
          \end{align}
  \end{itemize}
\end{lem}
\begin{proof}
  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and form degree. The $E_{1}$ page is the $d+\delbar$ cohomology and is given by the symmetric algebra on
\[
\begin{tikzcd}
\ul{\rm even} & \ul{\rm odd} \\
H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}}) \ar[r, "\del_{\Omega}"] & \H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) \ar[r, "\del_{\Omega}"] \
H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T^{*}_{\C^{5}}) \ar[l, "\del"]
\end{tikzcd}
.\]

>>>>

\[
\begin{tikzcd}
  &  \ul{\rm even} & \ul{\rm odd} \\
 \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
 \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
& \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}\end{tikzcd}
.\]

@@

          where $a, b, c, k, l \geq 0$.
    \item $V_{\mu}$ is spanned by
          \begin{align}
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{1}},\
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l-1}\del_{z_{1}}\text{ where }a > 0, b,c,k,l \geq 0 \\
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,b-1,c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{2}}, \ \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(0,b-1,c)}w_{1}^{k}w_{2}^{l-1}\del_{z_{2}}\text{ where }b > 0,c,k,l \geq 0 \\
            & \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,0,c-1)}w_{1}^{k-1}w_{2}^{l}\del_{z_{3}}, \ \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-l\delta^{(0,0,c-1)}w_{1}^{k}w_{2}^{l-1}\del_{z_{3}}\text{ where } c > 0,k,l \geq 0 \\
            & \delta^{(0,0,0)}w_{2}^{l}\del_{w_1}, \ \delta^{(0,0,0)}w_{1}^{k}\del_{w_2}\text{ where }k,l \geq 0
          \end{align}
  \end{itemize}
\end{lem}
\begin{proof}
  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and holomorphic form degree. The $E_{1}$ page is the $d+\dbar$ cohomology and is given by the symmetric algebra on

  \[
\begin{tikzcd}
\ul{\rm even} & \ul{\rm odd} \\
H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}})) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) )\\
H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3},  \iota^{*}T^{*}_{\C^{5}}))& H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO)) \ar[l, "\del"]
\end{tikzcd}
.\]
